Mahotas: Open source software for scriptable computer vision

### 2012-11-20 paper.tex
MIN Breakup lines to fit better on page
STYL Adjust look for arXiv

\documentclass{article}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{python}
\usepackage[%
    natbib=true,%
    useprefix=true,
    backend=biber,%
    backref=true,%
    citestyle=authoryear-comp,%
    bibstyle=authoryear,%
    maxbibnames=24,%
    maxcitenames=2,%
]{biblatex}

\hypersetup{%
    bookmarks=true,
    colorlinks=true,
    pdfauthor={Luis Pedro Coelho},
    citecolor=pondgreen,
    urlcolor=toastedchilipowder,
    linkcolor=toastedchilipowder,
}
\newcommand*{\cpp}{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\textbf{++}}}}
\let\code\texttt
\addbibresource{references.bib}

\title{Mahotas: Open source software for scriptable computer vision}
\author{Luis Pedro Coelho\\
Lane Center for Computational Biology, Carnegie Mellon University\\
Instituto de Medicina Molecular}

@@

Mahotas is available under a liberal open source license (MIT License) and is
available from \url{http://github.com/luispedro/mahotas} or the Python Package
Index (\url{http://pypi.python.org/pypi/mahotas}).

>>>>

\documentclass{scrartcl}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{python}
\usepackage{fontspec}
\usepackage[%
    natbib=true,%
    useprefix=true,
    backend=biber,%
    backref=true,%
    citestyle=authoryear-comp,%
    bibstyle=authoryear,%
    maxbibnames=24,%
    maxcitenames=2,%
]{biblatex}

\hypersetup{%
    bookmarks=true,
    colorlinks=true,
    pdftitle={Mahotas: Open source software for scriptable computer vision},
    pdfauthor={Luis Pedro Coelho},
    citecolor=pondgreen,
    urlcolor=toastedchilipowder,
    linkcolor=toastedchilipowder,
}
\font\CodeFont="DejaVu Sans Mono" at 8pt
\setmainfont[Mapping=tex-text]{Linux Libertine O}
\newcommand*{\cpp}{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\textbf{++}}}}
\def\code#1{\bgroup\CodeFont #1\egroup}
\addbibresource{references.bib}

\title{Mahotas: Open source software for scriptable computer vision}
\author{Luis Pedro Coelho\\
Lane Center for Computational Biology, Carnegie Mellon University\\
Instituto de Medicina Molecular}
\date{September 2012}

@@

Mahotas is released under a liberal open source license (MIT License) and is
available from \url{http://github.com/luispedro/mahotas} and from the Python Package
Index (\url{http://pypi.python.org/pypi/mahotas}).
